Les besoins en éducation pour les pratiques opensource

### 2022-09-08 main.tex
bib: prepare a way to indirectly cite publications cited by meta-analysis
lit. review: start reading about oss projects in CS education
review: make the document more presentable
appendices: include the data collection code
existing_teaching: rewrite and move to introduction
experiment: begin data analysis
manuscript: do a bit of cleaning and TODO-resolving
results: improve the presentation and start to write
results: almost finish the results and discussion part
introduction: finish the introduction
document: start the page count at the title page
document: ditch the unneeded custom \engl com

% Suppress some compilation warnings
\RequirePackage[save,showerrors]{silence}
\WarningFilter{biblatex}
  {The starred command '\DeclareDelimAlias*' is} % APA package is using this deprecated starred version
\WarningFilter{transparent}
  {Loading aborted} % I can't find where it is loaded, probably somewhere in kao's cls or sty
\WarningFilter{latex}
  {Unused global option} % They are, but kaobook is silently passing them to its base class
\WarningFilter{latex}
  {Marginpar on page} % Margin stuff moved to not overlap with other stuff, this is fine
\WarningFilter{latex}
  {There were undefined references} % seems spurious, no undefined references are reported
\WarningFilter{biblatex}
  {Please (re)run Biber on the file} % linked to the previous warning

@@

% Main and default language is french but there are some parts in english
\usepackage[main=french,english]{babel}
\newcommand{\en}[1]{\foreignlanguage{english}{\itshape #1}}
\usepackage{csquotes}
\MakeOuterQuote{"}

@@

% Bibliography configuration
\usepackage[style=apa]{kaobiblio}
\DefineBibliographyExtras{french}{\restorecommand\mkbibnamefamily}
\addbibresource{references.bib}

% Hyperref integration
\usepackage{kaorefs}

@@

% Configure the index and the glossary
\makeindex[columns=3, title=Alphabetical Index, intoc]
\makeglossaries
\setglossarystyle{altlist} % TODO: switch to altlistgroup if I end up with a lot entries
\input{glossary}
% shortcut for english glossary entries
\newcommand{\engl}[1]{\en{\gls{#1}}}
\newcommand{\enGl}[1]{\en{\Gls{#1}}}
\newcommand{\englpl}[1]{\en{\glspl{#1}}}
\newcommand{\enGlpl}[1]{\en{\Glspl{#1}}}

% Deactivate the citation/figure margin for new part pages
\NewCommandCopy{\oldaddpart}{\addpart}
\renewcommand{\addpart}[1]{%
    \pagelayout{wide} % no citation/figure margin
    \oldaddpart{#1}
    \pagelayout{margin} % restore the margin
}

>>>>

% Suppress some compilation warnings
\RequirePackage[save,showerrors]{silence}
\WarningFilter{biblatex}
  {The starred command '\DeclareDelimAlias*' is} % APA package is using this deprecated starred version
\WarningFilter{transparent}
  {Loading aborted} % Used by the svg package
\WarningFilter{latex}
  {Unused global option} % They are, but kaobook is silently passing them to its base class
\WarningFilter{latex}
  {Marginpar on page} % Margin stuff moved to not overlap with other stuff, this is fine
\WarningFilter{latex}
  {There were undefined references} % seems spurious, no undefined references are reported
\WarningFilter{biblatex}
  {Please (re)run Biber on the file} % linked to the previous warning

@@

% Code highlighting
\usepackage{minted}

% Main and default language is french but there are some parts in english
\usepackage[main=french,english]{babel}
\newcommand{\en}[1]{\foreignlanguage{english}{\emph{#1}}}
\usepackage{csquotes}
\MakeOuterQuote{"}

@@

% Bibliography configuration
\usepackage[style=apa,autolang=other]{kaobiblio}
\DefineBibliographyExtras{french}{\restorecommand\mkbibnamefamily}
\addbibresource{references.bib}
% Properly cite articles indirectly cited via meta-analysis, this mimics the \nocitemeta command from apacite
\DeclareBibliographyCategory{meta}
\renewbibmacro*{begentry}{\ifcategory{meta}{\ensuremath{{}^\ast}}{}}
\newcommand*{\nocitemeta}[1]{\nocite{#1}\addtocategory{meta}{#1}}

% Hyperref integration
\usepackage{kaorefs}
\usepackage[nobiblatex]{xurl}

% For typesetting hypothesis
\usepackage[framed=true, hypothesisbackground=gray!20!white]{kaotheorems}
\usepackage{thmtools}
\usepackage{thm-restate}

% For file inclusion and figure formatting
\usepackage{svg} % for svg images
\usepackage{caption}
\usepackage{subcaption}
\usepackage{pdfpages}

@@

% Configure the index and the glossary
\makeindex[columns=3, title=Alphabetical Index, intoc]
\makeglossaries
\setglossarystyle{altlist}
\AtBeginDocument{\input{glossary}} % Use AtBeginDocument to enable csquotes' MakeOuterQuote in descriptions

% Hyphenation
\hyphenation{Git-Hub}

% Use arabic numbers for the footnotes
\renewcommand{\thefootnote}{\arabic{footnote}}
